\documentclass{ximera}
%% handout
%% nohints
%% space
%% newpage
%% numbers

\input{preamble.tex} %% we can turn off input when making a master document

\outcome{Use an improper integral in an application problem.}
\outcome{Integrate a force function to compute work.}
\outcome{Correctly handle units during calculus operations.}

\title{Escape Velocity}
\begin{document}
\begin{abstract}
We start with Newton's law of gravitation and derive the escape velocity of a planet.
\end{abstract}
\maketitle


\begin{exercise}
Let's find a function $f(x)$ so that $f(2) = 4$.

\begin{solution}
\begin{hint}
Try a linear function.
\end{hint}
An example is $f(x) = $ \begin{expression-answer}
  function validator(f) {

    if (f.variables().indexOf('x') == -1) {
      feedback( 'You should include an $x$ in your answer.' );
    }

    if (f.variables().length > 1) {
      feedback( 'The only variable you should use is $x$.' );
    }

    if (Math.abs(f.evaluate( {x:2} ) - 4.0) < 0.0001) {
      return 1;
    }

    feedback( 'Check what happens when you plug in $x=2$.' );

    return 0;
  }
\end{expression-answer}.
\end{solution}

That is a great example.
\end{exercise}


\begin{observation}
\textbf{Newton's Law of Gravitation.} The force of gravity on an object of mass $m$ that is distance $r$ from the center of the earth is given by
$$ F(r) = \frac{G M m}{r^2}$$
where $G$ is the universal gravitational constant and $M$ is the mass of the Earth. In the metric system, the units of $G M$ are $\frac{m^3}{s^2}$.
\end{observation}

\begin{question}
Use the following two facts to find the value of $GM$ in $\frac{m^3}{s^2}$ to three significant digits. 
\begin{observation} A 100-kg object weighs 981 N at the surface of the Earth. \end{observation}
\begin{observation} The Earth's radius is 6380 km. \end{observation}

\begin{solution}
\begin{hint}
The two facts from this question can be plugged into the law of gravity.
\end{hint}
\begin{hint}
There is a problem with the units of the Earth's radius. Make sure you convert it to meters!
\end{hint}
\begin{hint}
Plugging in the values gives $981 N = \frac{GM (100 kg)}{(6380000 m)^2}$, so solve for $GM$.
\end{hint}
$GM =$ \answer{$3.99 * 10^{14}$} $\frac{m^3}{s^2}$.
\end{solution}
\end{question}

\begin{question}
The value of $G$ is $6.67 \cdot 10^{-11} \frac{m^3}{kg \cdot s^2}$. Find the mass of the Earth in kilograms. Give 3 significant digits.
\begin{solution}
\begin{hint}
You found the value of $G M$ in the previous question, so you should now be able to find M by dividing.
\end{hint}
\begin{hint}
Dividing $G M$ by $G$ and find 3 significant digits. 
\end{hint}
$M =$ \answer{$5.99*10^{24}$} $kg$.
\end{solution}
\end{question}


\end{document}
